Out-of-Sample Comparisons of Overfit Models

### 2016-03-09 paper.tex
[#49] Add code to generate and import Git info into LaTeX files
This commit adds code to the makefile to generate a (short) new file VERSION.tex
with information on the repository version (if the commit is tagged) or commit.
That imformation is included as the date and header of the final pdfs.
[#49] Tweak formatting and display of Git commit info
The commit information (date and hash) is posted in the header
of each page.
Include appendix with main paper for convenience to referees

\documentclass[12pt,draft]{article}
\input{VERSION}
\input{setup}

@@

@@

Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use out-of-sample (OOS) instead of in-sample
comparisons: the DMW OOS test%
\footnote{In this paper, we will refer to the basic OOS $t$-test
  studied by \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
allows a forecaster to conduct
inference about the expected future accuracy of his or her models when
one or both is overfit.  We show analytically and through Monte Carlo simulations
that standard full-sample test statistics can not test hypotheses
about this performance.

@@

Although OOS comparisons have been popular in Macroeconomics and
Finance since \citepos{MeR:83} seminal study of exchange rate models,
it has been unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using OOS comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the $F$-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular OOS test statistics under conditions
that would justify these full-sample tests.  Much
of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons \citep[see][for a
review of this literature]{Wes:06}.%
\footnote{Like us, \citet{Ana:07} allows the number of regressors to
  increase with $T$.  But in that paper, the number of regressors
  increases slowly enough that the OLS coefficients are consistent and
  asymptotically normal.} %
\citet{GiW:06} and
\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
derive an OOS test for the null hypothesis that the difference
between two models' OOS forecasting performance is unpredictable, a
martingale difference sequence (MDS); \citet{GiR:09} test whether the OOS
forecasting performance of a model suffers from a breakdown relative
to its in-sample performance; and \citet{GiR:10} test whether the
forecasting performance is stable. However, those papers focus on a
particular OOS estimation strategy and do not address why OOS
comparisons might be useful as a general strategy.

@@

We focus on linear regression models estimated with a fixed window
for simplicity, but our basic conclusions should be true for other
models and estimation strategies as well.  Under this
asymptotic theory, where the number of regressors $K$ increases with $T$
so that the limit of $K/T$ is positive and less than one,
the OLS coefficient estimator is no longer
consistent or asymptotically normal \citep{Hub:73} and has positive
variance in the limit.  We show that, even so, the usual OOS average
is asymptotically normal and can consistently estimate the difference
between the models' generalization error, the expected loss in the
future conditional on the data available in period
$T$.%
\footnote{See, for example, \citet{HTF:08} for a discussion of
  generalization error.} %
Under these asymptotics, the generalization
error does not converge to the expected performance of the pseudotrue
models, so existing in-sample and OOS comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our limit theory,
the model that is closer to the true DGP in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an OOS comparison would correctly fail to reject the null that the
benchmark is more accurate.%
\footnote{In a pair of papers similar to
  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
  the larger model has nonzero coefficients that are too close to zero
  to expect the model to forecast more accurately.  Like this paper,
  they argue that the larger model can be true but less accurate.
  However, they focus on an aspect of the DGP that makes this
  phenomenon likely, while we focus on the coefficient estimates that
  produce less accurate forecasts.  Moreover, the implications of our
  asymptotic theories are different and their papers do not provide
  reasons to do OOS comparisons.} %
Also note that, in this situation, a model that performs well
in-sample can perform badly out-of-sample even if there are no
structural breaks or other forms of instability.  Researchers
have argued that a breakdown of in-sample forecasting ability
indicates a structural break (see \citealp{BoH:99}, and
\citealp{StW:03}, among others), but we show that this breakdown
can be caused by overfit as well.

@@

Popular in-sample tests and model selection criteria, like the Wald
test and the AIC, do not help forecasters in this setting. We show
that these statistics do not select the more accurate model when
choosing between overfit models. For many DGPs the Wald test
will choose the larger model over a small benchmark
with probability much greater than its nominal size, regardless of
which model is more accurate, and the AIC behaves similarly. The BIC,
however, chooses the benchmark model with probability approaching one
even when the \emph{alternative} model is more accurate.%
\footnote{Our result holds for a broad class of full-sample
  statistics, but there may be other potential statistics that mimic
  the OOS test and remain valid. Exploring such statistics is left for
  future research.} %
This result holds even though modifications of the $F$-test are valid
under this asymptotic theory, as shown by \citet{BoB:95},
\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
among others.%
\footnote{Also see \citet{Efr:86,Efr:04} for a discussion of naive
  in-sample loss comparisons.} %
Moreover, under this asymptotic theory, many recent OOS test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
problems as in-sample tests.%
\footnote{Our theoretical results apply directly to \citepos{Mcc:07}
  OOS $t$-test, since it simply proposes more liberal critical values
  for the same test statistic that we study.  Since
  \citet{ClW:06,ClW:07} use a finite length estimation window, our
  asymptotics are incompatible with theirs and prevent us from
  studying their test directly, as well as \citepos{GiW:06} and other
  tests based on \citepos{GiW:06} asymptotics.  But \clws\ test can be
  viewed as a stochastic adjustment to the critical values of the
  usual \oost\ test, so our conclusions should apply informally as
  well.  Specifically, we show that the DMW test rejects with
  probability equal to nominal size when the estimated benchmark model
  is expected to be more accurate, so more liberal critical values
  result in overrejection.} %
These tests are also designed to reject the benchmark when the
alternative model is true, and so they may reject too often when the
benchmark is misspecified but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the DMW test when $P$ is small, but should overreject the benchmark
when $P$ is large. Section~\ref{sec:insample} presents our theoretical
results for full-sample statistics and Section~\ref{sec:mc} presents
Monte Carlo evidence to support these claims.

@@

In the settings we are interested in, a forecaster observes the data
$(y_t,x_t)$ for periods 1 through $T$ and divides these observations
into an estimation sample of the first $R$ observations and a test
sample of the remaining $P$ observations. The forecaster then compares
the models' performance over the test sample, which entails
constructing two sequences of forecasts with a fixed-window
estimation strategy,
\begin{equation*}
\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
\ t = R+1,\dots,T-h,
\end{equation*}
where
\begin{equation*}
  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
  x_{is} y_{s+\h}, \qquad \text{for } i=1,2;\ t = R+1,\dots, T - \h.%
\footnote{It may not be clear why we are using the index $t$ in $\bh{it}$,
    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
    But $\bh{it}$ will be defined for $t > T-\h$
    soon and will not equal $\bh{iR}$ for those values of $t$.} %
\end{equation*}

The models are then compared by their forecast performance over the test
sample. There are many statistics that have been considered in the
literature, but we focus on perhaps the most natural, the DMW \oost\
test \citep{DiM:95,Wes:96}.%
\footnote{The core insights of our paper apply to other OOS statistics
  as well.} %
This statistic is based on
the difference in the models' loss over the test sample, $\oosA$,
defined as
\begin{equation*}
  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
\end{equation*}
where
\begin{equation*}
  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
\end{equation*}
and $L$ is a known loss function. The \oost\ test is defined as
$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
Autocorrelation-Consistent, or HAC, estimator.)

Statistics like $\oost$ have a long history in empirical economics
because they capture an intuitive idea of model fit: that a good model
should be able to forecast well on new data. \cite{MeR:83}
use such a statistic to study exchange rate models and find that none
of the models that existed at the time of their study outperform a
random walk. This finding has been remarkably durable and has spawned
an enormous literature; see \cite{Mar:95}, \cite{KiT:03},
\cite{CCP:05}, \cite{EnW:05}, \cite{Ros:05}, and \cite{BWB:10}, among
many others. Research in financial markets has found a similar pattern,
e.g. \cite{BoH:99}, \citet{GoW:08,GoW:03}, and \citet{Tim:08}.

@@

Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
converge in probability to the difference in the expected loss
associated with the pseudotrue models,%
\footnote{This statement is subject to the usual assumptions: some
  form of stationarity, bounded moments, and weak dependence.} %
\begin{equation}\label{eq:22}
  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
\end{equation}
But if $K_2$ increases with $T$ these quantities can have different
limits. For a simple example, assume squared-error loss, let $x_{1,t}
= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
\Sigma)$.  Then the difference between $\E_T \oosB$ and
the in quantity~\eqref{eq:22} is
\begin{align*}
  \E_T \oosB - \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}&) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 -
     \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) \\
     &\quad - \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
  &= (\bh{2,t} - \theta_2)' \var(x_{2,t})\, (\bh{2,t} - \theta_2) + o_p(1).
\end{align*}
This last term has expectation equal to $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
would converge to zero in probability if $K_2$ were fixed, but does not when $\lim
K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
statistic can estimate $\E_T \oosB$ under our increasing $K$
asymptotics and does not estimate the expected loss associated with
the pseudotrue coefficients.

@@

Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
satisfies the CLT. Mixingales satisfy a weak-dependence condition
similar to MDSes,%
\footnote{An array $Z_{n,t}$ and an increasing sequence of \sfields
  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
  an array of constants $\{c_{n,t}\}$ and a sequence of constants
  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
  \begin{equation*}
    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
    \leq c_{n,t} \zeta_l
    \qquad\text{and}\qquad
    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
    \leq c_{n,t} \zeta_{l+1}.
  \end{equation*}
  Mixingales were introduced and developed by
  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
but they have some limitations. Transformations of mixingales are
typically not themselves mixingales, which means that CLTs for
mixingale processes require additional assumptions to hold beyond the
mixingale property.%
\footnote{See \citet{Jon:97} for an illustration. We will borrow
  heavily from his results in our proofs.} %
This is in contrast to Near Epoch Dependent (NED) processes, which
retain the NED property after transformations. \citep[See chapter 17
of][for further discussion of these properties.]{Dav:94} But the OOS
loss has more structure than most mixingales and behaves like an NED
process in important respects. (The key result here is
Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
CLT that we use later, and Section~\ref{sec:example} works through an
i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
MDS and is easier to work with.

@@

In this subsection we look at the behavior of some full-sample
statistics under the same asymptotic theory as before.  We show that
these statistics, which include common tests such as the Wald test as
well as model selection criteria such as the AIC, do not measure the
models' generalization error and consequently do not indicate which
model will be more accurate in the future. Some of these statistics
will tend to choose the larger model regardless of which model will be
more accurate in the future, whereas others tend to choose the smaller
model.  This is a different issue than whether or not full-sample
tests are valid for testing hypotheses about the pseudotrue
coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
demonstrate, variations of the Wald test can be valid for those
hypotheses under increasing-$K$ asymptotics.%
\footnote{\citet{Ana:12} shows that the Wald test is invalid in
  general and gives an adjustment that corrects the critical values;
  he also shows that the $F$-test is asymptotically valid under
  certain conditions on the distribution of the regressors.
  \citet{Cal:11c} shows that the $F$-test is asymptotically invalid
  without Anatolyev's constraint, even under homoskedasticity, and
  provides a correction that gives valid tests.  Both papers only
  consider independent observations.} %
To simplify the presentation and the intuition we only derive results
for nested models and for MSE loss, but the conclusions hold much more
generally.%
\footnote{In this section, we define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
  and $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
  selection matrices that return the first $K_1$ and the last $K_2 -
  K_1$ elements of $\theta_2$, and assume that the regressors are
  ordered so that the first $K_1$ elements of $x_{2,t}$ correspond to
  $x_{1,t}$.} %

@@

We look at four different statistics---the full-sample $F$-test, the
DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
values,%
\footnote{These critical values are not published for $K_2-K_1>10$, so
  we do not report them for $K_2 = T/10$.} %
and Clark and West's (2006, 2007) Gaussian out-of-sample statistic.%
\footnote{Clark and West (2006, 2007) derive their statistic using the
  rolling window estimation scheme. Here we use the same statistic,
  but with a fixed window scheme. A supplemental appendix presents
  results for their statistic, using the recursive window.} %
For the $F$-test, we simply test whether the coefficients on the
larger model are nonzero.  For the out-of-sample tests, we conduct a
one-sided test of out-of-sample performance for every value of $P$ as
before. For each of these simulations, we discard draws from the DGP
that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
remaining samples to calculate the conditional probability that each
test rejects. The simulations end when 2000 draws have been retained
for each choice of the design parameters.

@@

Since the DMW test tends to have low rejection probability, the test's
power is a concern.  Figure~\ref{fig:ttest-power} power results for
the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
to the constraint that $\E_T \oosB > 0$.%
\footnote{Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare
  when $c=0$, so we do not present results for that value of $c$.} %
Since the other test statistics greatly overreject, we do not present
their power.  For $c=1$, the power is never greater than nominal size
and decreases to zero as $P/T$ increases for the overfit model.  For
$c=2$ the power is better, increasing with $P/T$ at first stretch and
then decreasing as $P/T$ grows beyond approximately 1/4 for the
overfit model.  Larger values of $T$ give a higher peak and greater
power overall, but the power still falls to nearly zero if $P/T$ is
too large (approximately 2/3 in our simulations).  The power with the
parsimonious model is typically quite low but greater than nominal
size for $c = 2$.

@@

In summary, we fail to reject the null that the benchmark prevailing
mean model is more accurate than the full model including all of
\citepos{GoW:08} predictors.  This result is consistent with Goyal and
Welch's original analysis.  Unlike Goyal and Welch, we attribute this
result, at least in part, to parameter uncertainty---the full sample
results indicate that there is a true predictive relationship between
some of these variables and the equity premium and the larger model
could predict better than the benchmark with enough data.%
\footnote{\citet{BWB:10} make a similar point about exchange rate
  models, but see also \citet{Chi:10} and \citet{Gia:10}.} %
These also indicate that combination or shrinkage estimators of the
full model have the potential to significantly improve on the benchmark.%
\footnote{See \citet{RaZ:12} for a recent review of this
  literature.} %

>>>>

\documentclass[12pt,draft]{article}
\input{setup}

@@

\date{\VERSION}

@@

Consider two sequences of length $P$ of prediction errors, the result
of forecasting the same variable with two different estimated models.
Both models are estimated with $R$ observations, collectively called
the {\em estimation window}, and are used to forecast an additional
$P$ observations, called the {\em test sample}.  There are $T$
observations in all, and $R+P=T$.  This paper introduces a new limit
theory for statistics constructed from these prediction errors
designed to approximate the behavior of the statistics when one of the
models is overfit.  In doing so, we provide a theoretical
justification for forecasters to use out-of-sample (OOS) instead of in-sample
comparisons: the DMW OOS test\footnote{%
  In this paper, we will refer to the basic OOS $t$-test studied by
  \citet{DiM:95} and \citet{Wes:96} as the DMW test.} %
allows a forecaster to conduct
inference about the expected future accuracy of his or her models when
one or both is overfit.  We show analytically and through Monte Carlo simulations
that standard full-sample test statistics can not test hypotheses
about this performance.

@@

Although OOS comparisons have been popular in Macroeconomics and
Finance since \citepos{MeR:83} seminal study of exchange rate models,
it has been unclear from a theoretical perspective whether or not the
statistics are useful.  Empirical researchers often cite ``overfit''
or ``instability'' as reasons for using OOS comparisons, as in
\citet{StW:03}, but neither term is precisely defined or formalized.
Compounding this problem, the asymptotic distributions of these
statistics are derived under conditions that rule out either
instability or overfit and allow a researcher to use a conventional
in-sample comparison---a variation of the $F$-test, for example.  As
\citet{InK:04} argue, the statistics themselves are designed to test
hypotheses that can be tested by these in-sample statistics.  For
example, \citet{DiM:95} and \citet{Wes:96} derive the limiting
distributions of many popular OOS test statistics under conditions
that would justify these full-sample tests.  Much
of the subsequent research by \citet{Mcc:00, Mcc:07}, \citet{CCS:01},
\citet{ClM:01,ClM:05}, \citet{CoS:02,CoS:04}, \citet{ClW:06,ClW:07},
\citet{Ana:07}, and others relaxes several of Diebold and Mariano's
and West's assumptions, but maintains the stationarity and dependence
conditions that permit in-sample comparisons \citep[see][for a
review of this literature]{Wes:06}.\footnote{%
  Like us, \citet{Ana:07} allows the number of regressors to increase
  with $T$.  But in that paper, the number of regressors increases
  slowly enough that the OLS coefficients are consistent and
  asymptotically normal.} %
\citet{GiW:06} and
\citet{GiR:09, GiR:10} are exceptions.  Instead of focusing on
hypotheses that can be tested by in-sample comparisons, \citet{GiW:06}
derive an OOS test for the null hypothesis that the difference
between two models' OOS forecasting performance is unpredictable, a
martingale difference sequence (MDS); \citet{GiR:09} test whether the OOS
forecasting performance of a model suffers from a breakdown relative
to its in-sample performance; and \citet{GiR:10} test whether the
forecasting performance is stable. However, those papers focus on a
particular OOS estimation strategy and do not address why OOS
comparisons might be useful as a general strategy.

@@

We focus on linear regression models estimated with a fixed window
for simplicity, but our basic conclusions should be true for other
models and estimation strategies as well.  Under this
asymptotic theory, where the number of regressors $K$ increases with $T$
so that the limit of $K/T$ is positive and less than one,
the OLS coefficient estimator is no longer
consistent or asymptotically normal \citep{Hub:73} and has positive
variance in the limit.  We show that, even so, the usual OOS average
is asymptotically normal and can consistently estimate the difference
between the models' generalization error, the expected loss in the
future conditional on the data available in period
$T$.\footnote{%
  See, for example, \citet{HTF:08} for a discussion of generalization
  error.} %
Under these asymptotics, the generalization
error does not converge to the expected performance of the pseudotrue
models, so existing in-sample and OOS comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our limit theory,
the model that is closer to the true DGP in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an OOS comparison would correctly fail to reject the null that the
benchmark is more accurate.\footnote{%
  In a pair of papers similar to ours, \citet{ClM:12,ClM:12b} study
  in-sample and OOS tests that the larger model has nonzero
  coefficients that are too close to zero to expect the model to
  forecast more accurately.  Like this paper, they argue that the
  larger model can be true but less accurate.  However, they focus on
  an aspect of the DGP that makes this phenomenon likely, while we
  focus on the coefficient estimates that produce less accurate
  forecasts.  Moreover, the implications of our asymptotic theories
  are different and their papers do not provide reasons to do OOS
  comparisons.} %
Also note that, in this situation, a model that performs well
in-sample can perform badly out-of-sample even if there are no
structural breaks or other forms of instability.  Researchers
have argued that a breakdown of in-sample forecasting ability
indicates a structural break (see \citealp{BoH:99}, and
\citealp{StW:03}, among others), but we show that this breakdown
can be caused by overfit as well.

@@

Popular in-sample tests and model selection criteria, like the Wald
test and the AIC, do not help forecasters in this setting. We show
that these statistics do not select the more accurate model when
choosing between overfit models. For many DGPs the Wald test
will choose the larger model over a small benchmark
with probability much greater than its nominal size, regardless of
which model is more accurate, and the AIC behaves similarly. The BIC,
however, chooses the benchmark model with probability approaching one
even when the \emph{alternative} model is more accurate.\footnote{%
  Our result holds for a broad class of full-sample statistics, but
  there may be other potential statistics that mimic the OOS test and
  remain valid. Exploring such statistics is left for future
  research.} %
This result holds even though modifications of the $F$-test are valid
under this asymptotic theory, as shown by \citet{BoB:95},
\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
among others.\footnote{%
  Also see \citet{Efr:86,Efr:04} for a discussion of naive in-sample
  loss comparisons.} %
Moreover, under this asymptotic theory, many recent OOS test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
problems as in-sample tests.\footnote{%
  Our theoretical results apply directly to \citepos{Mcc:07} OOS
  $t$-test, since it simply proposes more liberal critical values for
  the same test statistic that we study.  Since \citet{ClW:06,ClW:07}
  use a finite length estimation window, our asymptotics are
  incompatible with theirs and prevent us from studying their test
  directly, as well as \citepos{GiW:06} and other tests based on
  \citepos{GiW:06} asymptotics.  But \clws\ test can be viewed as a
  stochastic adjustment to the critical values of the usual \oost\
  test, so our conclusions should apply informally as well.
  Specifically, we show that the DMW test rejects with probability
  equal to nominal size when the estimated benchmark model is expected
  to be more accurate, so more liberal critical values result in
  overrejection.} %
These tests are also designed to reject the benchmark when the
alternative model is true, and so they may reject too often when the
benchmark is misspecified but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the DMW test when $P$ is small, but should overreject the benchmark
when $P$ is large. Section~\ref{sec:insample} presents our theoretical
results for full-sample statistics and Section~\ref{sec:mc} presents
Monte Carlo evidence to support these claims.

@@

In the settings we are interested in, a forecaster observes the data
$(y_t,x_t)$ for periods 1 through $T$ and divides these observations
into an estimation sample of the first $R$ observations and a test
sample of the remaining $P$ observations. The forecaster then compares
the models' performance over the test sample, which entails
constructing two sequences of forecasts with a fixed-window
estimation strategy,
\begin{equation*}
\hat y_{i,t+\h} = x_{it}'\hat{\theta}_{it}, \qquad \text{for } i=1,2;
\ t = R+1,\dots,T-h,
\end{equation*}
where
\begin{equation*}
  \bh{it} = \Big(\sum_{s=1}^{R-\h} x_{is}x_{is}'\Big)^{-1} \sum_{s=1}^{R-\h}
  x_{is} y_{s+\h}, \qquad
  \text{for } i=1,2;\ t = R+1,\dots, T - \h.\footnote{%
    It may not be clear why we are using the index $t$ in $\bh{it}$,
    since $\bh{it} = \bh{iR}$ almost surely for all $t \leq T-h$.
    But $\bh{it}$ will be defined for $t > T-\h$
    soon and will not equal $\bh{iR}$ for those values of $t$.} %
\end{equation*}

The models are then compared by their forecast performance over the test
sample. There are many statistics that have been considered in the
literature, but we focus on perhaps the most natural, the DMW \oost\
test \citep{DiM:95,Wes:96}.\footnote{%
  The core insights of our paper apply to other OOS statistics as
  well.} %
This statistic is based on
the difference in the models' loss over the test sample, $\oosA$,
defined as
\begin{equation*}
  \oosA \equiv P^{-1} \oosSum{t}{1} D_t
\end{equation*}
where
\begin{equation*}
  D_t = L(y_{t+\h} - x_{1t}'\bh{1t}) - L(y_{t+\h} - x_{2t}'\bh{2t}),
\end{equation*}
and $L$ is a known loss function. The \oost\ test is defined as
$\sqrt{P} \oosA / \sh$, where $\sh^2$ is an estimator of the
asymptotic variance of $\oosA$. (Possibly a Heteroskedasticity- and
Autocorrelation-Consistent, or HAC, estimator.)

@@

Under conventional fixed-$K$ asymptotic theory, $\E_T \oosB$ would
converge in probability to the difference in the expected loss
associated with the pseudotrue models,\footnote{%
  This statement is subject to the usual assumptions: some form of
  stationarity, bounded moments, and weak dependence.} %
\begin{equation}\label{eq:22}
  \E L(y_{t+\h} - x_{1t}'\theta_{1}) - \E L(y_{t+\h} - x_{2t}'\theta_{2}).
\end{equation}
But if $K_2$ increases with $T$ these quantities can have different
limits. For a simple example, assume squared-error loss, let $x_{1,t}
= 1$ for all $t$, and let $(y_{t+\h},x_{2,t})$ be i.i.d. $N(0,
\Sigma)$.  Then the difference between $\E_T \oosB$ and
the in quantity~\eqref{eq:22} is
\begin{align*}
  \E_T \oosB - \big(\E L(y_{t+\h} - x_{1t}'\theta_{1}&) - \E L(y_{t+\h} - x_{2t}'\theta_{2})\big) \\
  &= \big(\E_T (y_{T+\h+1} - \bh{1,T})^2 -
     \E_T (y_{T+\h+1} - x_{T+1}'\bh{2,T})^2\big) \\
     &\quad - \big(\E y_{T+\h+1}^2 - \E (y_{T+\h+1} - x_{T+1}'\theta_2)^2 \big)\\
  &= (\bh{2,t} - \theta_2)' \var(x_{2,t})\, (\bh{2,t} - \theta_2) + o_p(1).
\end{align*}
This last term has expectation equal to $\var(y_T) \frac{K_2}{T - K_2 - 1}$ and
would converge to zero in probability if $K_2$ were fixed, but does not when $\lim
K_2 / T > 0$. In Section~\ref{sec:oostheory} we show that the \oost\
statistic can estimate $\E_T \oosB$ under our increasing $K$
asymptotics and does not estimate the expected loss associated with
the pseudotrue coefficients.

@@

Instead, we show that $D_t - \E_R D_t$ is an $L_2$-mixingale that
satisfies the CLT. Mixingales satisfy a weak-dependence condition
similar to MDSes,\footnote{%
  An array $Z_{n,t}$ and an increasing sequence of \sfields
  $\Gs_{n,t}$ is an \emph{$L_2$-mixingale of size $-1/2$} if there is
  an array of constants $\{c_{n,t}\}$ and a sequence of constants
  $\zeta_l = O(l^{-1/2 - \delta})$ for some $\delta > 0$ such that
  \begin{equation*}
    \lVert \E(Z_{n,t} \mid \Gs_{n,t-l}) \rVert_2
    \leq c_{n,t} \zeta_l
    \qquad\text{and}\qquad
    \lVert Z_{n,t} - \E(Z_{n,t} \mid \Gs_{n,t+l}) \rVert_2
    \leq c_{n,t} \zeta_{l+1}.
  \end{equation*}
  Mixingales were introduced and developed by
  \citet{Mcl:74,Mcl:75,Mcl:75b,Mcl:77}.} %
but they have some limitations. Transformations of mixingales are
typically not themselves mixingales, which means that CLTs for
mixingale processes require additional assumptions to hold beyond the
mixingale property.\footnote{%
  See \citet{Jon:97} for an illustration. We will borrow heavily from
  his results in our proofs.} %
This is in contrast to Near Epoch Dependent (NED) processes, which
retain the NED property after transformations. \citep[See chapter 17
of][for further discussion of these properties.]{Dav:94} But the OOS
loss has more structure than most mixingales and behaves like an NED
process in important respects. (The key result here is
Lemma~\ref{lem:a2} in the Appendix.) Lemma~\ref{res-mixingale} presents the
CLT that we use later, and Section~\ref{sec:example} works through an
i.i.d. example in detail. For i.i.d. observations, the OOS loss is an
MDS and is easier to work with.

@@

In this subsection we look at the behavior of some full-sample
statistics under the same asymptotic theory as before.  We show that
these statistics, which include common tests such as the Wald test as
well as model selection criteria such as the AIC, do not measure the
models' generalization error and consequently do not indicate which
model will be more accurate in the future. Some of these statistics
will tend to choose the larger model regardless of which model will be
more accurate in the future, whereas others tend to choose the smaller
model.  This is a different issue than whether or not full-sample
tests are valid for testing hypotheses about the pseudotrue
coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
demonstrate, variations of the Wald test can be valid for those
hypotheses under increasing-$K$ asymptotics.\footnote{%
  \citet{Ana:12} shows that the Wald test is invalid in general and
  gives an adjustment that corrects the critical values; he also shows
  that the $F$-test is asymptotically valid under certain conditions
  on the distribution of the regressors.  \citet{Cal:11c} shows that
  the $F$-test is asymptotically invalid without Anatolyev's
  constraint, even under homoskedasticity, and provides a correction
  that gives valid tests.  Both papers only consider independent
  observations.} %
To simplify the presentation and the intuition we only derive results
for nested models and for MSE loss, but the conclusions hold much more
generally.\footnote{%
  In this section, we define
  $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$ and
  $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
  selection matrices that return the first $K_1$ and the last
  $K_2 - K_1$ elements of $\theta_2$, and assume that the regressors
  are ordered so that the first $K_1$ elements of $x_{2,t}$ correspond
  to $x_{1,t}$.} %

@@

We look at four different statistics---the full-sample $F$-test, the
DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
values,\footnote{%
  These critical values are not published for $K_2-K_1>10$, so we do
  not report them for $K_2 = T/10$.} %
and Clark and West's (2006, 2007) Gaussian out-of-sample
statistic.\footnote{%
  Clark and West (2006, 2007) derive their statistic using the rolling
  window estimation scheme. Here we use the same statistic, but with a
  fixed window scheme. A supplemental appendix presents results for
  their statistic, using the recursive window.} %
For the $F$-test, we simply test whether the coefficients on the
larger model are nonzero.  For the out-of-sample tests, we conduct a
one-sided test of out-of-sample performance for every value of $P$ as
before. For each of these simulations, we discard draws from the DGP
that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
remaining samples to calculate the conditional probability that each
test rejects. The simulations end when 2000 draws have been retained
for each choice of the design parameters.

@@

Since the DMW test tends to have low rejection probability, the test's
power is a concern.  Figure~\ref{fig:ttest-power} power results for
the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
to the constraint that $\E_T \oosB > 0$.\footnote{%
  Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare when $c=0$,
  so we do not present results for that value of $c$.} %
Since the other test statistics greatly overreject, we do not present
their power.  For $c=1$, the power is never greater than nominal size
and decreases to zero as $P/T$ increases for the overfit model.  For
$c=2$ the power is better, increasing with $P/T$ at first stretch and
then decreasing as $P/T$ grows beyond approximately 1/4 for the
overfit model.  Larger values of $T$ give a higher peak and greater
power overall, but the power still falls to nearly zero if $P/T$ is
too large (approximately 2/3 in our simulations).  The power with the
parsimonious model is typically quite low but greater than nominal
size for $c = 2$.

@@

In summary, we fail to reject the null that the benchmark prevailing
mean model is more accurate than the full model including all of
\citepos{GoW:08} predictors.  This result is consistent with Goyal and
Welch's original analysis.  Unlike Goyal and Welch, we attribute this
result, at least in part, to parameter uncertainty---the full sample
results indicate that there is a true predictive relationship between
some of these variables and the equity premium and the larger model
could predict better than the benchmark with enough data.\footnote{%
  \citet{BWB:10} make a similar point about exchange rate models, but
  see also \citet{Chi:10} and \citet{Gia:10}.} %
These also indicate that combination or shrinkage estimators of the
full model have the potential to significantly improve on the
benchmark.\footnote{%
  See \citet{RaZ:12} for a recent review of this literature.} %
